%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%############


\begin{document}

%----------HEADER----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ahsanul Haque Munna} \\ \vspace{1pt}
    \small +880 17010 59628 $|$ \href{mailto:ahmunna.developer@gmail.com}{\underline{ahmunna.developer@gmail.com}} $|$ 
    \href{https://ah-munna.github.io}{\underline{ah-munna.github.io}} $|$
    \href{https://github.com/ah-munna}{\underline{github.com/ah-munna}}
\end{center}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Asian University of Bangladesh}{Ashulia}
      {Bachelor of Science in Computer Science \& Engineering}{2017 -- 2022}
    \resumeSubheading
      {BAF Shaheen College}{Dhaka}
      {Higher Secondary School Certificate, Science}{2014 -- 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Independent Software Developer}{Remote}
      {Freelance Automation Engineer}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Developed custom automation suites using Python, Tkinter, and Playwright for a digital marketing client.}
        \resumeItem{Reduced manual workflow time by \textbf{80\%} and helped double client revenue through process optimization.}
        \resumeItem{Engineered "Vampire Space Survivor," a simulation game using Godot, managing complex state logic and physics.}
        \resumeItem{Conducted \textbf{R\&D} on Large Language Models (LLMs) to build a self-conversational AI system.}
      \resumeItemListEnd

    \resumeSubheading
      {Nexis Limited}{Dhaka, Bangladesh}
      {Fullstack Web Developer}{Aug. 2023 -- June 2024}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable SaaS applications using Django, TypeScript, React, Next.js, and Prisma.}
        \resumeItem{Optimized database schemas, significantly enhancing feature sets and query performance for high-traffic products.}
        \resumeItem{Collaborated with cross-functional teams to integrate secure SSO (Single Sign-On) solutions.}
      \resumeItemListEnd

    \resumeSubSubheading
     {Frontend Developer}{Mar. 2023 -- Aug. 2023}
     \resumeItemListStart
        \resumeItem{Built responsive web pages using React.js and Next.js, ensuring cross-browser compatibility.}
        \resumeItem{Resolved critical bugs and maintained frontend architecture for internal tools.}
     \resumeItemListEnd

    \resumeSubSubheading
     {Frontend Developer Intern}{Dec. 2022 -- Mar. 2023}
     \resumeItemListStart
        \resumeItem{Assisted in the development of core web application modules using React.js and Next.js.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{\textbf{Projects}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Jahan Academy (EdTech Platform)} $|$ \emph{Next.js, NeonDB, NextAuth, Tailwind}}{Current}
          \resumeItemListStart
            \resumeItem{Architecting a comprehensive quiz platform for middle-school students to track academic progress.}
            \resumeItem{Implementing secure authentication via NextAuth and a high-performance database layer using NeonDB.}
            \resumeItem{Building a reactive teacher dashboard for real-time student analytics and grade management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Thesis Project Management System} $|$ \emph{Next.js, TypeScript, Prisma}}{2023}
          \resumeItemListStart
            \resumeItem{Developed a full-stack application to manage thesis submissions for the Asian University of Bangladesh.}
            \resumeItem{Streamlined the approval workflow between students and supervisors, replacing manual paper trails.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Chatting Platform} $|$ \emph{Next.js, tRPC, TypeScript, Prisma, Vercel AI SDK}}{2025}
          \resumeItemListStart
            \resumeItem{An AI chat application built with the T3 Stack and Vercel AI SDK.}
            \resumeItem{This platform provides a rich, immersive environment for users to interact with AI characters using custom personas, dynamic scenarios, and advanced chat features.}
            \resumeItem{Actively updating with robust future plans. \href{https://ai-ah-munna.vercel.app/}{\underline{live url}} \href{https://github.com/AH-Munna/ai-agent-platform}{\underline{github}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, C++, SQL} \\
     \textbf{Frameworks}{: React, Next.js, Django, Tailwind CSS, Bootstrap} \\
     \textbf{Tools}{: Git, Docker, Prisma, Linux, VS Code} \\
     \textbf{Concepts}{: Competitive Programming, Data Structures \& Algorithms, REST APIs}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{\textbf{Certifications}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Shikho Technologies}{: Fullstack Python and JavaScript Development Course (2021)}
    }}
    \small{\item{
     \textbf{IUPC}{: GUB Inter-University Programming Contest (2018), SUST Inter-University Programming Contest (2018)}
    }}
    \small{\item{
     \textbf{ICPC}{: DIU ICPC 2018 Asia Regional}
    }}
    \small{\item{
     \textbf{Problem Solving}{: \href{https://codeforces.com/profile/munna33}{\underline{codeforces}} \href{https://www.hackerrank.com/profile/AH_Munna}{\underline{hackerrank}}}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}